Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-21 doc/asplos13/evaluation.tex
some notes about plots

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism, which both systems depend on.
\TODO{data from our trace would be nice here}. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves
\checkme{112Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node. Grappa's scaling slows down at
\checkme{90} machines because of the unscalability of our aggregation
mechanism as there are more network endpoints.

@@

>>>>

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism, which both systems depend on.
\TODO{data from our trace would be nice here}. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves
\checkme{112Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node. Grappa keeps scaling up through 128
machines, although scaling declines because of the unscalability of our aggregation
mechanism as number of network endpoints increases.

@@

%\begin{figure*}[ht]
%    \begin{minipage}{0.3\linewidth}
%        \centering
%        \includegraphics[width=\textwidth]{figs/chunksize-uts.pdf}
%        \caption{chunksize caption}
%        \label{fig:chunksize-uts}
%    \end{minipage}
%    \begin{minipage}{0.3\linewidth}
%        \centering
%        \includegraphics[width=\textwidth]{figs/workers-uts.pdf}
%        \caption{workers caption}
%        \label{fig:workers-uts}
%    \end{minipage}
%    \begin{minipage}{0.3\linewidth}
%        \centering
%        \includegraphics[width=\textwidth]{figs/thresh-uts.pdf}
%        \caption{threshold caption}
%        \label{fig:thresh-uts}
%    \end{minipage}
%\end{figure*}

Chunksize:
amortizing cost of stealing
spreading work out more
most of the time we still little  (about 10 avg) but sometimes a lot
(difference with BFS)
